Unrecognized States: Theory and Cases

### 2017-07-03 theory.tex
strip math out of Def 1 and a few other misc locations as proof of concept

\begin{enumerate} 
\item $p$ chooses an investment level $R_p^t\in \left[0,B_p^t\right]$ to influence the payoffs of $s$ and $g$, where $B_p^t$ is an exogenous limit on the finances of the patron.

\item $c$ chooses an investment level $R_c^t\in \mathbb{R}^+$ to influence the payoffs of $s$ and $g$.

@@

The payoffs at the end of a period are determined by these actions and six state variables. These state variables keep track of the value of the status quo ($Q_s^t$ and $Q_g^t$), losing ($L_s^t$ and $L_g^t$) and winning the issue of status ($W_s^t$ and $W_g^t$) for the secessionists and government respectively. The transitions of the state variables are described below.

@@

\begin{definition}
\emph{The class $\mathcal{G}$ includes all those games for which the parameters satisfy the following restrictions:}

\begin{enumerate}
\item \textit{For both players $g$ and $s$, $Q_i^0 \geq L_i^0$: remaining in the status quo is better than ceding at the beginning of the game.}\label{res:1}

\item \textit{For both players $g$ and $s$, $\frac {Q_i^0}{1-\delta} \geq \frac {\omega_i^0}{1-\delta} = -\zeta_i+\frac{W_i^0(p_i) + L_i^0(1-p_i)}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}\label{res:2}

\item \textit{Either (a) $\frac{L_s^0}{1-\delta}  > \frac{\omega_s^0}{1-\delta}$ or (b) $0 > -\mu > \frac{\lambda p_s - \alpha (1-p_s)}{1-\de}$: either the secessionists prefer ceding to war or the patron's disutility from war is greater than the per-period cost of offsetting the deterioration in the secessionists' status quo payoffs.}\label{res:new}

\item \textit{$\frac{\alpha}{1-\de} \geq \frac{\beta}{1-\de} + \mu$: reunification is more important for the patron to avoid than for the international community to achieve.}\label{res:3}

\item  \textit{$\nu\cdot p_s \geq \lambda \cdot p_s + \mu + \beta$: recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve.}\label{res:4}

\item  \textit{$B_p^1 \geq\frac{\beta}{1-\delta} - \left(Q_s^0 -\mu - L_s^0 \right)$: the patron can afford to deter player $c$ from inducing reunification at the beginning of the game.}\label{res:5}

\item \textit{$B_p^t \geq \mu, \ \forall t$: the patron can afford to pay to maintain the status quo.}\footnote{Depending on parameters, one might think that Restriction (5) is more likely to be binding than Restriction (6). If there is great variance in budget between periods for the patron, such as a greatly reduced budget in some period $t> 1$ compared to period $1$, (6) could be the binding constraint.}\label{res:6}

@@

Our concept of equilibrium will be stationary Markov equilibrium as defined in Mailath and Samuelson (2006). That is, a strategy profile is a stationary Markov equilibrium if it is a stationary Markov strategy profile and a subgame-perfect equilibrium. In turn, a strategy profile is defined to be a stationary Markov strategy if any two ex post histories terminating in the same state play identically from the termination point forward. In other words, stationary Markov strategies ignore all details of the history aside from the current state.

The state is a vector of six variables comprised of the payoffs from the status quo, ceding, and winning the issue of status for each of the two inside actors. That is, $s = \left(Q_s,Q_g,L_s,L_g,W_s,W_g \right)$.\footnote{In the case of $W_s^t$ and $W_g^t$, it is more intuitive to imagine investments increasing the probability of winning a war; because the lottery is additively separable and the ``Win'' outcome is always preferred when it occurs independently in the stage game, this more convenient modeling choice is inconsequential.} Strategies for the patron and the international community are how much to invest in each of the six state variables. However, positive investments in some of the state variables can be ruled out by preference assumptions.

>>>>

\begin{enumerate} 
\item $p$ chooses an investment level to influence the payoffs of $s$ and $g$.

\item $c$ chooses an investment level to influence the payoffs of $s$ and $g$.

@@

The payoffs at the end of a period are determined by these actions and six state variables. These state variables keep track of the value of the status quo, losing and winning the issue of status for the secessionists and government respectively.

@@

\begin{definition}
\emph{The class $\mathcal{G}$ includes all those games for which following restrictions are satisfied:}

\begin{enumerate}
\item \textit{For both players $g$ and $s$, remaining in the status quo is better than ceding at the beginning of the game.}\label{res:1}

\item \textit{For both players $g$ and $s$, the expected outcome under war is worse than the status quo at the beginning of the game.}\label{res:2}

\item \textit{Either the secessionists prefer ceding to war or the patron's disutility from war is greater than the per-period cost of offsetting the deterioration in the secessionists' status quo payoffs.}\label{res:new}

\item \textit{Reunification is more important for the patron to avoid than for the international community to achieve.}\label{res:3}

\item  \textit{Recognition of the secessionist state is more important for the international community to avoid than for the patron to achieve.}\label{res:4}

\item  \textit{The patron can afford to deter player $c$ from inducing reunification at the beginning of the game.}\label{res:5}

\item \textit{The patron can afford to pay to maintain the status quo.}\label{res:6}

@@

Our concept of equilibrium will be stationary Markov equilibrium as defined in Mailath and Samuelson (2006). Strategies in a stationary Markov equilibrium ignore all details of the history aside from the current state.

The state is a vector of six variables comprised of the payoffs from the status quo, ceding, and winning the issue of status for each of the two inside actors. That is, $s = \left(Q_s,Q_g,L_s,L_g,W_s,W_g \right)$.
